---
title: "Regression Project"
author: "Sam Ibrahim"
date: "November 2, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
if(!require("rglwidget")) {install.packages("rglwidget");require("rglwidget")}
data <- read.csv(file = "http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep = "",header = TRUE)
```

```{r}
plot(SIMS~ARM,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point(aes(col=ARM)) 
```

```{r}
cor(SIMS~ARM,data=data)
```

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
basicNN + geom_point(aes(col=ARM)) + geom_smooth(method=lm)
```

```{r}
x=data.frame(GRIP=94, ARM=88)
predict.lm(model.1,x,interval = "prediction")
```

The 95% predictions intervals are between .706-3.13

Now for the SIMs the function of GRIP

```{r}
plot(SIMS~GRIP,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point(aes(col=GRIP)) 
```

```{r}
cor(SIMS~GRIP,data=data)
```

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

```{r}
basicNN + geom_point(aes(col=GRIP)) + geom_smooth(method=lm)
```

```{r}
x=data.frame(GRIP=94, ARM=88)
predict.lm(model.2,x,interval = "prediction")
```

The 95% predictions intervals are between -.536-2.035


Now for the SIMs the function of ARM+GRIP


```{r}
plot(SIMS~ARM+GRIP,data=data,xlab="ARM+GRIP")
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM+GRIP))
```

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point(aes(col=ARM+GRIP)) 
```

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

```{r}
basicNN + geom_point(aes(col=ARM+GRIP)) + geom_smooth(method=lm)
```

```{r}
x=data.frame(GRIP=94, ARM=88)
predict.lm(model.3,x,interval = "prediction")
```


```{r}
a=anova(model.1,model.3)
print(a)
str(a)
```

$H_0$ We fail to reject the null hypothesis showing that there is no difference between arm strength vs. arm+grip strength

$H_0$ We reject the null hypothesis showing that there is a difference between arm strength vs. arm+grip strength

We reject the null hypothesis based on the evidence we have it with a Pvalue of 4.994e-06 which is less than .05 and the model that predicts simulations that uses arm+grip is a better model for the simulations that uses arm only.